The evolution of gene expression in the term placenta of viviparous mammals

### 2016-04-04 manuscript/manuscript.Rnw
it's SOLD1 not SORD1

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \sheep are shown in
\cref{tab:top50_sheep_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_ovis_aries_placenta}. The complete
list of highly expressed genes includes many snRNAs and rRNAs likely
due to the RNA extraction and library preparation procedure utilized
for this sample. Ignoring these, notable highly expressed genes
include members of annexin complexes
(\Sexpr{gene.expression("ovis_aries","S100G",complete=TRUE)},
\Sexpr{gene.expression("ovis_aries","ANXA2",complete=TRUE)}),
hemoglobin subunits
(\Sexpr{gene.expression("ovis_aries","ENSOARG00000010944",complete=TRUE)}),
an ortholog of \textit{SSLP1},
\Sexpr{gene.expression("ovis_aries","SORD1",complete=TRUE)}, two
cathespins (\Sexpr{gene.expression("ovis_aries","CTSL",complete=TRUE)}
and \Sexpr{gene.expression("ovis_aries","CTSB",complete=TRUE)}), and
placentally expressed transcript 1
\Sexpr{gene.expression("ovis_aries","PLET1",complete=TRUE)} which may
play a role in cellular migration
\cite{Raymond.ea2010:Expressionoforphanprotein}.

>>>>

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \sheep are shown in
\cref{tab:top50_sheep_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_ovis_aries_placenta}. The complete
list of highly expressed genes includes many snRNAs and rRNAs likely
due to the RNA extraction and library preparation procedure utilized
for this sample. Ignoring these, notable highly expressed genes
include members of annexin complexes
(\Sexpr{gene.expression("ovis_aries","S100G",complete=TRUE)},
\Sexpr{gene.expression("ovis_aries","ANXA2",complete=TRUE)}),
hemoglobin subunits
(\Sexpr{gene.expression("ovis_aries","ENSOARG00000010944",complete=TRUE)}),
an ortholog of \textit{SSLP1},
\Sexpr{gene.expression("ovis_aries","SOLD1",complete=TRUE)}, two
cathespins (\Sexpr{gene.expression("ovis_aries","CTSL",complete=TRUE)}
and \Sexpr{gene.expression("ovis_aries","CTSB",complete=TRUE)}), and
placentally expressed transcript 1
\Sexpr{gene.expression("ovis_aries","PLET1",complete=TRUE)} which may
play a role in cellular migration
\cite{Raymond.ea2010:Expressionoforphanprotein}.
